Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-11-28 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
summary of metaheuristic approach in related work reformulated

@@

Another study has presented a data mining approach to generate an initial population for population-based heuristics/metaheuristics to solve JSP \cite{nasiri2019data}. They extracted information from optimal or near-optimal solutions obtained by a heuristic procedure called "Assignment Procedure" to build decision rules to determine the priority of the operations. Once the rules are extracted, the initial solution is generated using these rules. To evaluate the performance of the proposed method, they performed a series of computational experiments on several test instances. The results showed that the proposed method with data mining generated initial population outperforms the methods with randomly generated initial population.

>>>>

The integration of dispatching rules generated with data mining techniques
into stochastic optimization in~\cite{nasiri2019data} works by
running a greedy algorithm called ``assignment procedure'' to obtain promising
JSP solutions and mine dispatching rules approximating them.
But instead of relying on the dispatching rules alone for computing optimized
schedules or performing efficient operation allocation on new instances,
the high-quality draft solutions from greedy search with the dispatching rules
are taken as inputs to population-based stochastic optimization.
This metaheuristic optimization was shown to yield improved outcomes when launched
with schedules generated by means of suitable dispatching rules rather than with
a randomly generated initial population.

@@

% Another study has presented a data mining approach to generate an initial population for population-based heuristics/metaheuristics to solve JSP \cite{nasiri2019data}. They extracted information from optimal or near-optimal solutions obtained by a heuristic procedure called "Assignment Procedure" to build decision rules to determine the priority of the operations. Once the rules are extracted, the initial solution is generated using these rules. To evaluate the performance of the proposed method, they performed a series of computational experiments on several test instances. The results showed that the proposed method with data mining generated initial population outperforms the methods with randomly generated initial population.
